Dissertation Title

### 2018-01-24 dissertation.tex
dissertation.lyx Imported from dissertation.tex ...

\documentclass{iuphd}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
\DeclareUnicodeCharacter{0229}{\c{e}}
\DeclareUnicodeCharacter{00A0}{~}
\usepackage{mmap}
\usepackage{comment}

%data for Title Page
\title{Dissertation Title}
\author{Author}
\date{Completion Date}

%data for Acceptance Page
\committeechair{Committee Chair}
\readertwo{2nd Reader}
\readerthree{3rd Reader}
\readerfour{4th Reader}
\defensedate{Defense Date}

%data for Copyright Page
\cryear{Current Year}

\begin{document}
\maketitle

\acceptancepage

\copyrightpage

@@

\begin{abstract}
 The abstract is double-spaced and limited to 350 words. As many people will learn about
your work through your abstract published in Dissertation Abstracts (http://proquest.umi.com/login),
you should spend a good bit of effort in the composition of both the abstract and the title of your work.
Try to convey the flavor of your work, not just the bare bones of your findings; in an average abstract
there will be about 70 characters per line with a maximum of 35 lines. You should also work to phrase your
title so that it truly describes the contents and will be easily found in the index of Dissertation Abstracts.
The index is based on key words, so be as specific as you can be about your subject. 
\end{abstract}

>>>>

\documentclass[twoside]{iuphd}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
\DeclareUnicodeCharacter{0229}{\c{e}}
\DeclareUnicodeCharacter{00A0}{~}
\usepackage{mmap}
\usepackage{comment}

\begin{document}
%data for Title Page
\begin{comment}
\title{Dissertation Title}
\author{Author}
\date{Completion Date}
\end{comment}
\title{Discrete Quantum Theories and Computing}
\author{Yu-Tsung Tai}
\date{\today}
\maketitle

%data for Acceptance Page
\committeechair{Committee Chair}
\readertwo{2nd Reader}
\readerthree{3rd Reader}
\readerfour{4th Reader}
\defensedate{Defense Date}
\acceptancepage

%data for Copyright Page
\begin{comment}
\cryear{Current Year}
\end{comment}
\cryear{2018}
\copyrightpage

@@

\begin{abstract}
\begin{comment}
 The abstract is double-spaced and limited to 350 words. As many people will learn about
your work through your abstract published in Dissertation Abstracts (http://proquest.umi.com/login),
you should spend a good bit of effort in the composition of both the abstract and the title of your work.
Try to convey the flavor of your work, not just the bare bones of your findings; in an average abstract
there will be about 70 characters per line with a maximum of 35 lines. You should also work to phrase your
title so that it truly describes the contents and will be easily found in the index of Dissertation Abstracts.
The index is based on key words, so be as specific as you can be about your subject.
\end{comment}
Our primary research interest is to build a quantum computing model
characterizing realistic quantum computers. While most of the quantum
computing models based on uncomputable numbers, that is, the continuum
of real numbers, most of the classical computers in our daily life
are digital instead of analog computers. This highlight the necessity
to investigate discrete models for quantum theory and computing. Specifically,
we start from replacing the continuum of complex numbers by the discrete
finite fields. Although we have fruitful results on their geometric
implications and computing powers, their probability models are still
not completely satisfactory. To address this issue, we further exploited
quantum interval-valued probability, and proved an imprecise version
of foundational results such as the Gleason and Kochen-Specker theorems.
\end{abstract}
